---
title: "Web Scraping Analytics"
author: "Po Yi Liu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(tidytext)
library(topicmodels)
library(wordcloud2)
library(readr)
library(stringr)
library(twitteR)
```

```{r}
# Declare Twitter API Credentials
api_key <- "your_key_here"
api_secret <- "your_secret_here" 
token <- "your_token_here" 
token_secret <- "your_token_secret_here" 
 
# Create Twitter Connection
setup_twitter_oauth(api_key, api_secret, token, token_secret)
```

```{r}
#Grab the last 10000 tweets
d_tweets<-searchTwitter("AI", n=10000, lang="en")

#Convert to a data frame
d_tweets_df <- twListToDF(d_tweets)

#Standardise text encoding
d_tweets_df$text <-
  str_conv(d_tweets_df$text, 'UTF-8')

saveRDS(d_tweets_df, 'D:/medium/web scraping analytics/twitter_search_dataset.RDS')
```


## Term Frequency & Wordcloud 

create tweet_freq table

1. create a month_varaible 
2. parse terms into words, remove the stopwords
3. summarize by month and word
4. take top 100 words by month 
```{r}
tweet_freq<-d_tweets_df%>%
  mutate(month = month(created))%>%
  unnest_tokens(word,text)%>%
  anti_join(get_stopwords())%>%
  filter(!word %in% c("t.co", "https", "false", "twitter", "iphone", "amp", 
                      "rt", "android","it's","like","love"))%>%
  group_by(month,word)%>%
  summarise(n=n())%>%
  top_n(100,n) 

tweet_freq
```


```{r}
tweet_freq%>%
  ungroup()%>%
  select(-month)%>%
  group_by(word)%>%
  summarise(n = sum(n))%>%
  ungroup()%>%
  wordcloud2(size = 2)
```


## Bigram Analysis 

create table bigram_freq by 
1. create a bigram 
2. summarize by bigram 
3. use separate to split bigram into word1 and word2 then filter the following
4. create a bigram varaible by combining word1 and word2 together 
5. wordcloud of top 100 bigram terms. 
6. make a chart of the top 20 terms that come after the word "new"
7. make a chart of the top 20 terms that come before the word "new"

```{r}
bigram_freq<-d_tweets_df%>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2, n_min = 2)%>%
  group_by(bigram)%>%
  summarise(n=n())%>%
  ungroup()%>%
  separate(bigram, c("word1", "word2"), sep = " ")%>%
  anti_join(stop_words,by = c("word1" = "word"))%>%
  anti_join(stop_words,by = c("word2" = "word"))%>%
  filter(!word1 %in% c("t.co", "https", "false", "twitter", "iphone", "amp", 
                      "rt", "android","it's","like","love"),
         !word2 %in% c("t.co", "https", "false", "twitter", "iphone", "amp", 
                      "rt", "android","it's","like","love"),
         !str_detect(word1,"^\\d"),
         !str_detect(word2,"^\\d"))%>%
  mutate(bigram = paste(word1,word2))%>%
  select(bigram,n)%>%
  arrange(desc(n))

bigram_freq
```


```{r}
bigram_freq%>%
  top_n(100,n)%>%
  wordcloud2(size = 0.5)
```


```{r}
bigram_freq%>%
  filter(str_detect(bigram,"^ai"))%>%
  top_n(20,n)%>%
  ggplot(aes(x=reorder(bigram, n),y=n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Frequency of ai", x="ai",y="counts")
```

```{r}
bigram_freq%>%
  filter(str_detect(bigram,"ai$"))%>%
  top_n(20,n)%>%
  ggplot(aes(x=reorder(bigram, n),y=n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Frequency of ai", x="ai",y="counts")
```



## Sentiments

create sentiment_by_month 
1. inner join words_by_month to "bing" sentiments 
2. group by month and sentiment 
3. get the top 10 words by month 
4. make words with negative sentiment negative (-n) and positive words positive


```{r}
sentiment_by_month <- tweet_freq %>%
  inner_join(get_sentiments("nrc")) %>%
  group_by(month,sentiment) %>%
  top_n(30,n)%>%
  mutate(n = if_else(sentiment == "negative", -n, n))

sentiment_by_month
```


```{r}
sentiment_by_month%>%
  filter(month==12)%>%
  ggplot(aes(reorder(word, n), n, fill=sentiment)) +
  geom_col() + 
  coord_flip() +
  labs(title = "Bing: Top and bottom 10 terms by sentiment in Jan", x = "term", y="count")
```


## Topic Prep 

Create tweet_dtm by preparing a Document Term Matrix

1. unest tokens into words 
2. remove the stop words
3. summarize by tweet id and word
4. take top 20 words by id 

```{r}
tweet_dtm<-d_tweets_df%>%
  unnest_tokens(word,text)%>%
  anti_join(get_stopwords())%>%
  filter(!word %in% c("t.co", "https", "false", "twitter", "iphone", "amp", 
                      "rt", "android","it's","like","love"))%>%
  group_by(id,word)%>%
  summarise(n=n())%>%
  top_n(20,n)
tweet_dtm
```


```{r}
tweet_dtm <- tweet_dtm %>% cast_dtm(id, word, n)
tweet_lda <- LDA(tweet_dtm, k = 10, method = "Gibbs", control = list(seed = 1234))
```


## Topic Model 

1. document term matrix needs to be cleaned up and generate beta 
2. generate topic terms by extracting top_n by beta 
3. plot the topics 

```{r}
tidy_tweet <- tidy(tweet_lda,matrix = "beta")

tweet_topic_terms <- tidy_tweet %>%
  group_by(topic) %>%
  filter(term != "it’s") %>%
  top_n(20,beta) %>%
  ungroup()%>%
  arrange(topic)

tweet_topic_terms

```

```{r}
tweet_topic_terms %>%
  mutate(term = reorder(term, beta)) %>%
  #ungroup() %>%
  arrange(desc(beta)) %>%  
  ggplot(aes(reorder(term, beta), beta, fill = as.factor(topic))) +
  geom_col(show.legend = FALSE, size = 0.5) +
  coord_flip() +
  labs(title = "Topic Terms",
       x = NULL, y = expression(beta)) + 
  facet_wrap(~ topic, ncol = 5, scales = "free")+
  theme(axis.text = element_text(size = 7))
```



